---
title: "Hu-sh1289-final"
Author: "Shanshan Hu"
output: html_document
---

# My github: https://github.com/ShanshanHoo/test/tree/geo
# Credit ? OpenStreetMap contributors

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## load the packages

```{r}
library(tidyverse)
library(rvest)   # rvest::zillow		Scrape housing info from tripadvisor
library(lubridate)
library(stringr)
library(broom) # For problem 3
library(stringi)
library(ggplot2)

library(RCurl)
library(XML)
library(ZillowR)

library(tidyr)
library(plyr)
library(dplyr)
library(readxl)
library(reshape2)
library(rgdal)
library(ggplot2)
library(rgeos)
library(raster)
library(sf)
library(leaflet)
library(reshape2)
library(data.table)
```

## Data source (1) Zillow

https://www.zillow.com/howto/api/APIOverview.htm
.	API Categories: Home Valuation, Property, Demographics, Mortgage Rates & Payment Estimates
.	Architectural Style: REST
.	Supported Request Formats: Unknown
.	Supported Response Formats: XML
http://www.zillow.com/webservice/GetRegionChildren.htm
https://www.zillow.com/research/data/
Geo zip file:
https://www.zillow.com/howto/api/neighborhood-boundaries.htm
United States and 50 Largest Metro Areas: This month
https://www.zillow.com/research/local-market-reports/

```{r}
set_zillow_web_service_id('X1-ZWz180j32k8qob_ako3m')


zillow_dwnload <- xmlParse("http://files.zillowstatic.com/") %>% xmlToList("Content")
zillow_dwnload <- unlist(zillow_dwnload, use.names = TRUE) %>% as_tibble()
zillow_dwnload <- subset(zillow_dwnload, grepl("^research/preview/Neighborhood", zillow_dwnload[[1]]))
zillow_dwnload <- zillow_dwnload$value %>% str_replace_all("preview", "public") %>% as_data_frame()

```

# Zillow from file

```{r}
library(jsonlite)
z0 <- fromJSON("http://files.zillowstatic.com/research/public/StaticFiles/Decade/Data/LatLongs/Philadelphia_2010.json")

z6 <- read_csv("http://files.zillowstatic.com/research/public/Neighborhood/Neighborhood_Zhvi_AllHomes.csv", col_names = TRUE) %>% subset(CountyName=="Philadelphia County") #county philadelphia
z6_1 <- read_csv(paste0("http://files.zillowstatic.com/", zillow_dwnload[74,1], sep=""), col_names = TRUE) %>% subset(CountyName=="Philadelphia County") %>% mutate("type"="1 bedroom")
z6_2 <- read_csv(paste0("http://files.zillowstatic.com/", zillow_dwnload[75,1], sep=""), col_names = TRUE) %>% subset(CountyName=="Philadelphia County") %>% mutate("type"="2 bedroom")
z6_3 <- read_csv(paste0("http://files.zillowstatic.com/", zillow_dwnload[76,1], sep=""), col_names = TRUE) %>% subset(CountyName=="Philadelphia County") %>% mutate("type"="3 bedroom")
z6_4 <- read_csv(paste0("http://files.zillowstatic.com/", zillow_dwnload[77,1], sep=""), col_names = TRUE) %>% subset(CountyName=="Philadelphia County") %>% mutate("type"="4 bedroom")
z6_5 <- read_csv(paste0("http://files.zillowstatic.com/", zillow_dwnload[78,1], sep=""), col_names = TRUE) %>% subset(CountyName=="Philadelphia County") %>% mutate("type"="5 bedroom and more")
z6_6 <- read_csv(paste0("http://files.zillowstatic.com/", zillow_dwnload[82,1], sep=""), col_names = TRUE) %>% subset(CountyName=="Philadelphia County") %>% mutate("type"="CondCoop")
z6_7 <- read_csv(paste0("http://files.zillowstatic.com/", zillow_dwnload[85,1], sep=""), col_names = TRUE) %>% subset(CountyName=="Philadelphia County") %>% mutate("type"="SingleFamily")

# read_csv(paste0("http://files.zillowstatic.com/", zillow_dwnload[2,1], sep=""), col_names = TRUE) %>% subset(CountyName=="Philadelphia County") #county philadelphia

z8 <- read_csv("http://files.zillowstatic.com/research/public/Neighborhood/Neighborhood_MedianListingPricePerSqft_AllHomes.csv", col_names = TRUE) %>% subset(CountyName=="Philadelphia County") #county philadelphia
z8_1 <- read_csv(paste0("http://files.zillowstatic.com/", zillow_dwnload[42,1], sep=""), col_names = TRUE) %>% subset(CountyName=="Philadelphia County") %>% mutate("type"="1 bedroom")
z8_2 <- read_csv(paste0("http://files.zillowstatic.com/", zillow_dwnload[43,1], sep=""), col_names = TRUE) %>% subset(CountyName=="Philadelphia County") %>% mutate("type"="2 bedroom")
z8_3 <- read_csv(paste0("http://files.zillowstatic.com/", zillow_dwnload[44,1], sep=""), col_names = TRUE) %>% subset(CountyName=="Philadelphia County") %>% mutate("type"="3 bedroom")
z8_4 <- read_csv(paste0("http://files.zillowstatic.com/", zillow_dwnload[45,1], sep=""), col_names = TRUE) %>% subset(CountyName=="Philadelphia County")#%>%mutate("type"="4 bedroom")
z8_5 <- read_csv(paste0("http://files.zillowstatic.com/", zillow_dwnload[46,1], sep=""), col_names = TRUE) %>% subset(CountyName=="Philadelphia County")#%>%mutate("type"="5 bedroom and more")
z8_6 <- read_csv(paste0("http://files.zillowstatic.com/", zillow_dwnload[48,1], sep=""), col_names = TRUE) %>% subset(CountyName=="Philadelphia County") %>% mutate("type"="CondCoop")
z8_7 <- read_csv(paste0("http://files.zillowstatic.com/", zillow_dwnload[49,1], sep=""), col_names = TRUE) %>% subset(CountyName=="Philadelphia County") %>% mutate("type"="SingleFamily")

z10 <- read_csv("http://files.zillowstatic.com/research/public/Neighborhood/Sale_Counts_Neighborhood.csv", col_names = TRUE) %>% mutate("type"="SaleCount")#only have region name and ID

z11 <- read_csv("http://files.zillowstatic.com/research/public/Neighborhood/Sale_Prices_Neighborhood.csv", col_names = TRUE) %>% mutate("type"="SalePrice")#only have region name and ID

z12 <- read_csv("http://files.zillowstatic.com/research/public/Neighborhood/InventoryMeasure_Neighborhood_Public.csv", col_names = TRUE) %>% subset(CountyName=="Philadelphia") #county philadelphia

z13 <- read_csv("http://files.zillowstatic.com/research/public/County/MarketHealthIndex_County.csv", col_names = TRUE) %>% subset(RegionName=="Philadelphia County")  #county philadelphia

z14 <- read_csv("http://files.zillowstatic.com/research/public/CountyCrossWalk_Zillow.csv", col_names = TRUE) #id and name look-up

z15 <- read_csv("http://files.zillowstatic.com/research/public/Neighborhood/NewMonthlyListings_SSA_AllHomes_Neighborhood.csv", col_names = TRUE)

z16 <- read_csv("http://files.zillowstatic.com/research/public/Neighborhood/MonthlyListings_SSA_AllHomes_Neighborhood.csv", col_names = TRUE)


z17 <- read_csv("http://files.zillowstatic.com/research/public/Neighborhood/MedianDailyListings_SSA_AllHomes_Neighborhood.csv", col_names = TRUE)

z18 <- read_csv("http://files.zillowstatic.com/research/public/Neighborhood/Neighborhood_MedianListingPrice_AllHomes.csv", col_names = TRUE) %>% subset(CountyName=="Philadelphia County") #county philadelphia

```



```{r}
zhvi_nbed <- rbind.data.frame(z6_1,z6_2,z6_3,z6_4,z6_5) %>% gather(Date, ZHVI, 8:283)
zhvi_nbed <- zhvi_nbed[rowSums(is.na(zhvi_nbed[,10]))!=1,]
zhvi_typ <- rbind.data.frame(z6_6,z6_7) %>% gather(Date, ZHVI, 8:283)
zhvi_typ <- zhvi_typ[rowSums(is.na(zhvi_typ[,10]))!=1,]

zlsprice_nbed <- rbind.fill(z8_1,z8_2,z8_3) %>% gather(Date, PPerSqft, 7:116)
zlsprice_nbed <- drop_na(zlsprice_nbed)
zlsprice_typ <- rbind.fill(z8_6,z8_7) %>% gather(Date, PPerSqft, 7:116)
zlsprice_typ <- drop_na(zlsprice_typ)


zregion_name <- z6 %>% dplyr::select("RegionID","RegionName")
zsale_count <- zregion_name %>% inner_join(z10) %>% mutate("type"="SaleCount")
zsale_price <- zregion_name %>% inner_join(z11) %>% mutate("type"="SalePrice")
zsale <- rbind.fill(zsale_count,zsale_price) %>% gather(Date, Value, 5:138) %>% drop_na()

z6 <- z6 %>% gather(Date, ZHVI, 8:283)
z6 <- drop_na(z6)
z6$Date <- z6$Date %>% parse_date_time("ym")#%>%format("%Y-%m")
z6 <- z6%>%mutate(Month = format(Date, "%m"), Year = format(Date, "%Y")) %>% group_by(Month, Year)

z8 <- z8 %>% gather(Date, PPerSqft, 7:117)
z8 <- drop_na(z8)
z8$Date <- z8$Date %>% parse_date_time("ym")#%>%format("%Y-%m")
z8 <- z8%>%mutate(Month = format(Date, "%m"), Year = format(Date, "%Y")) %>% group_by(Month, Year)

z18 <- z18 %>% gather(Date, Price, 7:117)
z18 <- drop_na(z18)
z18$Date <- z18$Date %>% parse_date_time("ym")#%>%format("%Y-%m")
z18 <- z18%>%mutate(Month = format(Date, "%m"), Year = format(Date, "%Y")) %>% group_by(Month, Year)

zexp_6 <- z6  %>% dplyr::select(Date, value=ZHVI,Month, Year) 
zexp_6 <- melt(setDT(zexp_6), id.vars = "Year", measure.vars = "value")[, mean(value), by = Year] %>% dplyr::mutate(type="ZHVI") 
zexp_18 <- z18 %>% dplyr::select(Date, value=Price,Month, Year)
zexp_18 <- melt(setDT(zexp_18), id.vars = "Year", measure.vars = "value")[, mean(value), by = Year] %>% dplyr::mutate(type="Pice")
zexp <- rbind(zexp_6,zexp_18)
```


```{r}
z6_plot <- ggplot() + geom_jitter(z6,mapping=aes(x=Year,y=ZHVI,color=RegionName),size=0.01) + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + scale_y_continuous(name="Zillow Home Value Index", labels = scales::comma)

z6_plot
ggsave("z6_plot_legend.png", dpi=1200, dev='png', height=4, width=5, units="in")
print(z6_plot + theme(legend.position = "none"))
ggsave("z6_plot.png", dpi=1200, dev='png', height=4, width=5, units="in")

z8_plot <- ggplot() + geom_jitter(z8,mapping=aes(x=Year,y=PPerSqft,color=RegionName),size=0.01) + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + scale_y_continuous(name="Median Listing Price PerSqft", labels = scales::comma, limits=c(0,700))
z8_plot
ggsave("z8_plot_legend.png", dpi=1200, dev='png', height=4, width=5, units="in")
print(z8_plot + theme(legend.position = "none"))
ggsave("z8_plot.png", dpi=1200, dev='png', height=4, width=5, units="in")

zexp_plot <- ggplot() + geom_line(zexp,mapping=aes(x=Year,y=V1,color=type,group=type),size=1) + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + scale_y_continuous(name="Zillow estimate V.S. Expectation", labels = scales::comma)
ggsave("zexp_plot.png", dpi=1200, dev='png', height=4, width=5, units="in")
```



```{r}
zhvi_nbed_lm <- zhvi_nbed %>% dplyr::select(-c(City,State,Metro,CountyName,SizeRank)) 
zhvi_nbed_lm_plot <- ggplot(zhvi_nbed_lm, mapping = aes(x=RegionName,y=ZHVI,color=type)) +
  geom_point() + 
  theme(axis.text.x = element_text(size = 2, angle = 90, hjust = 1)) + 
  scale_y_continuous(name="Zillow Home Value Index", labels = scales::comma)

zhvi_typ_lm <- zhvi_typ %>% dplyr::select(-c(City,State,Metro,CountyName,SizeRank)) 
zhvi_typ_lm_plot <- ggplot(zhvi_typ_lm, mapping = aes(x=RegionName,y=ZHVI,color=type)) +
  geom_point() + 
  theme(axis.text.x = element_text(size = 2, angle = 90, hjust = 1)) + 
  scale_y_continuous(name="Zillow Home Value Index", labels = scales::comma)

```



```{r}
# I manually checked the source html to find how to turn photocard page
#links <- sprintf("https://www.zillow.com/homes/Philadelphia-PA_rb/%d_p", 1:20)  

links <- paste0('https://www.zillow.com/homes/?searchQueryState={%22mapBounds%22:{%22west%22:-75.38788418457034,%22east%22:-74.84818081542971,%22south%22:39.845515939525285,%22north%22:40.159388222934766},%22usersSearchTerm%22:%22Philadelphia%20PA%22,%22regionSelection%22:[{%22regionId%22:13271,%22regionType%22:6}],%22isMapVisible%22:true,%22mapZoom%22:11,%22filterState%22:{%22isNewConstruction%22:{%22value%22:false},%22isForSaleForeclosure%22:{%22value%22:false},%22isComingSoon%22:{%22value%22:false},%22isAuction%22:{%22value%22:false},%22isPreMarketForeclosure%22:{%22value%22:false},%22isPreMarketPreForeclosure%22:{%22value%22:false},%22isMakeMeMove%22:{%22value%22:false},%22isRecentlySold%22:{%22value%22:true}},%22isListVisible%22:true,%22pagination%22:{%22currentPage%22:', 1:20, "}}", sep="")

z_photocard <- map(links, ~ {

         houses <- read_html(.x) %>%
                html_nodes(".photo-cards li article")
         z_id <- houses %>% 
                    html_attr("id")

         address <- houses %>%
                html_node(".zsg-photo-card-address") %>%
                html_text()

         price <- houses %>%
             html_node(".zsg-photo-card-price") %>%
             html_text() %>%
             readr::parse_number()

        params <- houses %>%
             html_node(".zsg-photo-card-info") %>%
             html_text() %>%
             strsplit("&middot;")

        beds <- params %>%
             str_extract("\\d+(?=\\s*bds)") %>%
             as.numeric()
        baths <- params %>% 
             str_extract("\\d+(?=\\s*ba)") %>%
             as.numeric()
        house_area <- params %>%
               str_extract("[0-9,]+(?=\\+*\\s*sqft)") %>%
               str_replace(",", "") %>%
               as.numeric

data_frame(price = price, beds= beds, baths=baths, house_area = house_area, id = z_id, address = address)

                 }
                 ) %>%

    bind_rows(.id = 'page_no')
 z_photocard <- drop_na(z_photocard)

```


###
$response
<response>
 <properties>
  <principal>
   <zpid>9396682</zpid>
   <links>
    <homedetails>https://www.zillow.com/homedetails/101-Dauphin-Dr-Media-PA-19063/9396682_zpid/</homedetails>
    <graphsanddata>http://www.zillow.com/homedetails/101-Dauphin-Dr-Media-PA-19063/9396682_zpid/#charts-and-data</graphsanddata>
    <mapthishome>http://www.zillow.com/homes/9396682_zpid/</mapthishome>
    <comparables>http://www.zillow.com/homes/comps/9396682_zpid/</comparables>
   </links>
   <address>
    <street>101 Dauphin Dr</street>
    <zipcode>19063</zipcode>
    <city>Media</city>
    <state>PA</state>
    <latitude>39.938598</latitude>
    <longitude>-75.367816</longitude>
   </address>
   <taxAssessmentYear>2018</taxAssessmentYear>
   <taxAssessment>295200.0</taxAssessment>
   <yearBuilt>2012</yearBuilt>
   <lotSizeSqFt>348088</lotSizeSqFt>
   <finishedSqFt>3652</finishedSqFt>
   <bathrooms>3.0</bathrooms>
   <bedrooms>3</bedrooms>
   <totalRooms>8</totalRooms>
   <lastSoldDate>01/02/2019</lastSoldDate>
   <lastSoldPrice currency="USD">528000</lastSoldPrice>
   <zestimate>
    <amount currency="USD">536435</amount>
    <last-updated>05/02/2019</last-updated>
    <oneWeekChange deprecated="true"/>
    <valueChange duration="30" currency="USD">2153</valueChange>
    <valuationRange>
     <low currency="USD">509613</low>
     <high currency="USD">563257</high>
    </valuationRange>
    <percentile>85</percentile>
   </zestimate>
   <localRealEstate>
    <region name="Marple" id="398683" type="city">
     <zindexValue>380,900</zindexValue>
     <links>
      <overview>http://www.zillow.com/local-info/PA-Marple/r_398683/</overview>
      <forSaleByOwner>http://www.zillow.com/marple-pa/fsbo/</forSaleByOwner>
      <forSale>http://www.zillow.com/marple-pa/</forSale>
     </links>
    </region>
   </localRealEstate>
  </principal>
  <comparables>
   <comp score="5.0">
    <zpid>2087177793</zpid>
    <links>
     <homedetails>https://www.zillow.com/homedetails/307-Avian-Media-PA-19063/2087177793_zpid/</homedetails>
     <mapthishome>http://www.zillow.com/homes/2087177793_zpid/</mapthishome>
     <comparables>http://www.zillow.com/homes/comps/2087177793_zpid/</comparables>
    </links>
    <address>
     <street>307 Avian</street>
     <zipcode>19063</zipcode>
     <city>Media</city>
     <state>PA</state>
     <latitude>39.941449</latitude>
     <longitude>-75.366754</longitude>
    </address>
    <finishedSqFt>2412</finishedSqFt>
    <bathrooms>4.0</bathrooms>
    <bedrooms>3</bedrooms>
    <lastSoldDate>10/30/2018</lastSoldDate>
    <lastSoldPrice currency="USD">421995</lastSoldPrice>
    <zestimate>
     <amount currency="USD">470987</amount>
     <last-updated>05/02/2019</last-updated>
     <oneWeekChange deprecated="true"/>
     <valueChange duration="30" currency="USD">-1290</valueChange>
     <valuationRange>
      <low currency="USD">386209</low>
      <high currency="USD">626413</high>
     </valuationRange>
     <percentile>0</percentile>
    </zestimate>
    <localRealEstate>
     <region name="Marple" id="398683" type="city">
      <zindexValue>380,900</zindexValue>
      <links>
       <overview>http://www.zillow.com/local-info/PA-Marple/r_398683/</overview>
       <forSaleByOwner>http://www.zillow.com/marple-pa/fsbo/</forSaleByOwner>
       <forSale>http://www.zillow.com/marple-pa/</forSale>
      </links>
     </region>
    </localRealEstate>
   </comp>
   <comp score="4.0">
    <zpid>2087223376</zpid>
    <links>
     <homedetails>https://www.zillow.com/homedetails/301-Corvus-Drive-Media-PA-19063/2087223376_zpid/</homedetails>
     <mapthishome>http://www.zillow.com/homes/2087223376_zpid/</mapthishome>
     <comparables>http://www.zillow.com/homes/comps/2087223376_zpid/</comparables>
    </links>
    <address>
     <street>301 Corvus Drive</street>
     <zipcode>19063</zipcode>
     <city>Media</city>
     <state>PA</state>
     <latitude>39.938611</latitude>
     <longitude>-75.366389</longitude>
    </address>
    <finishedSqFt>3000</finishedSqFt>
    <bathrooms>3.0</bathrooms>
    <bedrooms>3</bedrooms>
    <lastSoldDate>10/26/2018</lastSoldDate>
    <lastSoldPrice currency="USD">423995</lastSoldPrice>
    <zestimate>
     <amount currency="USD">514747</amount>
     <last-updated>05/02/2019</last-updated>
     <oneWeekChange deprecated="true"/>
     <valueChange duration="30" currency="USD">-3712</valueChange>
     <valuationRange>
      <low currency="USD">401503</low>
      <high currency="USD">612549</high>
     </valuationRange>
     <percentile>0</percentile>
    </zestimate>
    <localRealEstate>
     <region name="Marple" id="398683" type="city">
      <zindexValue>380,900</zindexValue>
      <links>
       <overview>http://www.zillow.com/local-info/PA-Marple/r_398683/</overview>
       <forSaleByOwner>http://www.zillow.com/marple-pa/fsbo/</forSaleByOwner>
       <forSale>http://www.zillow.com/marple-pa/</forSale>
      </links>
     </region>
    </localRealEstate>
   </comp>
   <comp score="4.0">
    <zpid>2090552161</zpid>
    <links>
     <homedetails>https://www.zillow.com/homedetails/311-Avian-Aly-Media-PA-19063/2090552161_zpid/</homedetails>
     <mapthishome>http://www.zillow.com/homes/2090552161_zpid/</mapthishome>
     <comparables>http://www.zillow.com/homes/comps/2090552161_zpid/</comparables>
    </links>
    <address>
     <street>311 Avian Aly</street>
     <zipcode>19063</zipcode>
     <city>Media</city>
     <state>PA</state>
     <latitude>39.938611</latitude>
     <longitude>-75.366388</longitude>
    </address>
    <finishedSqFt>2295</finishedSqFt>
    <bathrooms>2.5</bathrooms>
    <bedrooms>3</bedrooms>
    <lastSoldDate>11/29/2018</lastSoldDate>
    <lastSoldPrice currency="USD">449926</lastSoldPrice>
    <zestimate>
     <amount currency="USD">440321</amount>
     <last-updated>05/02/2019</last-updated>
     <oneWeekChange deprecated="true"/>
     <valueChange duration="30" currency="USD">-22059</valueChange>
     <valuationRange>
      <low currency="USD">356660</low>
      <high currency="USD">550401</high>
     </valuationRange>
     <percentile>0</percentile>
    </zestimate>
    <localRealEstate>
     <region name="Marple" id="398683" type="city">
      <zindexValue>380,900</zindexValue>
      <links>
       <overview>http://www.zillow.com/local-info/PA-Marple/r_398683/</overview>
       <forSaleByOwner>http://www.zillow.com/marple-pa/fsbo/</forSaleByOwner>
       <forSale>http://www.zillow.com/marple-pa/</forSale>
      </links>
     </region>
    </localRealEstate>
   </comp>
   <comp score="4.0">
    <zpid>2090932091</zpid>
    <links>
     <homedetails>https://www.zillow.com/homedetails/303-Avian-Aly-Media-PA-19063/2090932091_zpid/</homedetails>
     <mapthishome>http://www.zillow.com/homes/2090932091_zpid/</mapthishome>
     <comparables>http://www.zillow.com/homes/comps/2090932091_zpid/</comparables>
    </links>
    <address>
     <street>303 Avian Aly</street>
     <zipcode>19063</zipcode>
     <city>Media</city>
     <state>PA</state>
     <latitude>39.938611</latitude>
     <longitude>-75.366388</longitude>
    </address>
    <finishedSqFt>2741</finishedSqFt>
    <bathrooms>2.5</bathrooms>
    <bedrooms>3</bedrooms>
    <lastSoldDate>11/28/2018</lastSoldDate>
    <lastSoldPrice currency="USD">447295</lastSoldPrice>
    <zestimate>
     <amount currency="USD">487119</amount>
     <last-updated>05/02/2019</last-updated>
     <oneWeekChange deprecated="true"/>
     <valueChange duration="30" currency="USD">-1985</valueChange>
     <valuationRange>
      <low currency="USD">394566</low>
      <high currency="USD">594285</high>
     </valuationRange>
     <percentile>0</percentile>
    </zestimate>
    <localRealEstate>
     <region name="Marple" id="398683" type="city">
      <zindexValue>380,900</zindexValue>
      <links>
       <overview>http://www.zillow.com/local-info/PA-Marple/r_398683/</overview>
       <forSaleByOwner>http://www.zillow.com/marple-pa/fsbo/</forSaleByOwner>
       <forSale>http://www.zillow.com/marple-pa/</forSale>
      </links>
     </region>
    </localRealEstate>
   </comp>
   <comp score="2.0">
    <zpid>2084804200</zpid>
    <links>
     <homedetails>https://www.zillow.com/homedetails/301-Murray-Media-PA-19063/2084804200_zpid/</homedetails>
     <mapthishome>http://www.zillow.com/homes/2084804200_zpid/</mapthishome>
     <comparables>http://www.zillow.com/homes/comps/2084804200_zpid/</comparables>
    </links>
    <address>
     <street>301 Murray</street>
     <zipcode>19063</zipcode>
     <city>Media</city>
     <state>PA</state>
     <latitude>39.9417</latitude>
     <longitude>-75.3664</longitude>
    </address>
    <finishedSqFt>2666</finishedSqFt>
    <bathrooms>3.0</bathrooms>
    <bedrooms>3</bedrooms>
    <lastSoldDate>02/08/2019</lastSoldDate>
    <lastSoldPrice currency="USD">489215</lastSoldPrice>
    <zestimate>
     <amount currency="USD">469340</amount>
     <last-updated>05/02/2019</last-updated>
     <oneWeekChange deprecated="true"/>
     <valueChange/>
     <valuationRange>
      <low currency="USD">380165</low>
      <high currency="USD">581982</high>
     </valuationRange>
     <percentile>0</percentile>
    </zestimate>
    <localRealEstate>
     <region name="Marple" id="398683" type="city">
      <zindexValue>380,900</zindexValue>
      <links>
       <overview>http://www.zillow.com/local-info/PA-Marple/r_398683/</overview>
       <forSaleByOwner>http://www.zillow.com/marple-pa/fsbo/</forSaleByOwner>
       <forSale>http://www.zillow.com/marple-pa/</forSale>
      </links>
     </region>
    </localRealEstate>
   </comp>
  </comparables>
 </properties>
</response>




## Data source (5)

https://www.census.gov/data/developers/data-sets/acs-5year.html
Base API call: 	https://api.census.gov/data/2017/acs/acs5/cprofile

```{r}
library(leaflet)
library(acs)
library(tidycensus)
library(choroplethr)
library(tigris)
library(sf)
#census_api_key("f1fdffa783c407597f3c93ee46cf1714ad0c6b7f",install = TRUE,overwrite=TRUE)
acs_t <- get_acs(geography = "tract", variables=c(house_value="B25075_001",total_unit="B25001_001",house_type="B11011_001",plumbing="B25047_001",kitchen="B25051_001",year_built="B25034_001",n_beds="B25041_001"),key="f1fdffa783c407597f3c93ee46cf1714ad0c6b7f",state = 42,county=101,geometry=TRUE)

# acs_page <- read_html("https://api.census.gov/data/2017/acs/acs5/cprofile/310?get=CP05_2013_2017_001E,NAME&for=metropolitan%20statistical%20area/micropolitan%20statistical%20area:10420&key=f1fdffa783c407597f3c93ee46cf1714ad0c6b7f")
# 
# find out what's tract, place, moe, ZCTA and how to get block

acs_t[which(acs_t$variable!='house_value'), ] %>% ggplot(aes(fill = estimate)) +
  facet_wrap(~variable) +
  geom_sf(color = NA) +
  coord_sf(crs = 26915) + 
  scale_fill_viridis_c(option = "A") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 


acs_tt <- acs_t[which(acs_t$variable!='house_value'), ] %>% dplyr::select(-moe)
acs_tt <- acs_tt %>% spread(key = variable, value = estimate)


acs_cor<- get_acs(geography = "tract", variables=c(total_unit="B25001_001",house_type="B11011_001",plumbing="B25047_001",kitchen="B25051_001",year_built="B25034_001",n_beds="B25041_001"),key="f1fdffa783c407597f3c93ee46cf1714ad0c6b7f",state = 42,county=101,geometry=FALSE)

acs_cor <- acs_cor %>% dplyr::select(-moe) %>% spread(key = variable, value = estimate)
acs_cor <- acs_cor %>% dplyr::select(house_type:year_built)
acs_cor_plot <- ggcorr(data = NULL, cor_matrix = cor(acs_cor, use = "everything"))

```



```{r echo = FALSE}
acs_value <- acs_t[which(acs_t$variable=='house_value'), ]
acs_value %>%
  ggplot(aes(fill = estimate)) + 
  geom_sf(color = NA) + 
  coord_sf(crs = 26911) + 
  scale_fill_viridis_c(option = "B") 

pal1 <- colorBin("Greens", domain = acs_value$estimate, n = 9)

acs_value %>%
    st_transform(crs = "+init=epsg:4326") %>%
    leaflet() %>%
    addProviderTiles(provider = "CartoDB.Positron") %>%
    addPolygons(popup = ~ str_extract(NAME, "^([^,]*)"),
                stroke = FALSE,
                smoothFactor = 0,
                fillOpacity = 1,
                color = ~ pal1(estimate)) %>%
    addLegend("bottomright", 
              pal = pal, 
              values = ~ estimate,
              title = "Median House Value",
              opacity = 1)
```




```{r}
api.key.install("f1fdffa783c407597f3c93ee46cf1714ad0c6b7f")

filled.contour(acs_value$geometry, color=rainbow,plot.axes=contour(acs_value$estimate, add=T))
```



