---
title: "unused cdoe"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(rvest)   # rvest::zillow		Scrape housing info from tripadvisor
library(lubridate)
library(stringr)
library(broom) # For problem 3
library(stringi)
library(ggplot2)

library(RCurl)
library(XML)
library(ZillowR)

library(tidyr)
library(plyr)
library(dplyr)
library(readxl)
library(reshape2)
library(rgdal)
```

## Zillow

```{r}
library(jsonlite)

zillow2 <- fromJSON("http://files.zillowstatic.com/research/public/StaticFiles/Decade/Data/LatLongs/Philadelphia_2010.json")

zillow3 <- read_csv("http://files.zillowstatic.com/research/public/County/County_MedianListingPricePerSqft_AllHomes.csv", col_names = TRUE) #%>% subset(State=="PA" & MunicipalCodeFIPS==101) #county philadelphia

zillow4 <- read_csv("http://files.zillowstatic.com/research/public/County/County_MedianValuePerSqft_AllHomes.csv", col_names = TRUE) #%>% subset(RegionID==3175) #county philadelphia

zillow5 <- read_csv("http://files.zillowstatic.com/research/public/County/County_Zhvi_AllHomes.csv", col_names = TRUE) #county philadelphia

```

# using rvest::zillow demo
# my search
https://www.zillow.com/homes/for_sale/Philadelphia-PA/fsba,fsbo,fore,new_lt/house,mobile,townhouse_type/13271_rid/3-_beds/1.5-_baths/0-600000_price/0-2390_mp/globalrelevanceex_sort/40.142664,-74.848824,39.814865,-75.439339_rect/10_zm/0_mmm/
# current listing in photo card 1st page
# demo

```{r}
# Inspired by https://github.com/notesofdabbler


page <- read_html(zp_urls$ad[2])

houses <- page %>%
  html_nodes(".photo-cards li article")
bind_rows(lapply(xml_attrs(houses), function(x) data.frame(as.list(x), stringsAsFactors=FALSE)))

z_id <- houses %>% html_attr("id")

address <- houses %>%
  html_node(".zsg-photo-card-address") %>%
  html_text()

price <- houses %>%
  html_node(".zsg-photo-card-price") %>%
  html_text() %>%
  readr::parse_number()

params <- houses %>%
  html_node(".zsg-photo-card-info") %>%
  html_text() %>%
  strsplit("\u00b7")

beds <- params %>% purrr::map_chr(1) %>% readr::parse_number()

baths <- params %>% purrr::map_chr(2) %>% readr::parse_number(default = "")

house_area <- params %>% purrr::map_chr(3) %>% readr::parse_number()

```


```{r}
zilow_dwnload <- xmlParse("http://files.zillowstatic.com/")%>%xmlToList()%>%select(Content$Key)%>%as_tibble()
#can only select one list
```

## Including Plots

You can also embed plots, for example:

```{r}
#
#  Explore Zillow data using rvest
# 
#  rvest package currently under development by Hadley Wickham
#  https://github.com/hadley/rvest
#

library(rvest)
library(magrittr)

# here the search is filtered to just homes for sale
# if there are less filters in search, the code will need to be modified since the css might be different
# for different types of results (eg. homes for sales vs new homes vs homes for rent)
url <- 'https://www.zillow.com/homes/?searchQueryState={"mapBounds":{"west":-75.38788418457034,"east":-74.84818081542971,"south":39.845515939525285,"north":40.159388222934766},"usersSearchTerm":"Philadelphia%20PA","regionSelection":[{"regionId":13271,"regionType":6}],"isMapVisible":true,"mapZoom":11,"filterState":{"isPreMarketForeclosure":{"value":false},"isPreMarketPreForeclosure":{"value":false},"isMakeMeMove":{"value":false}},"isListVisible":true,"pagination":{"currentPage":2}}'

# get list of houses for sales that appears on the page
houselist <- url%>%html()%>%html_node("article")

# Extract zillow id for each listing
zpid <- houselist%>%html_attr("id")

# get the address for each listing
staddrlink <- houselist%>%html_node(".property-address a")%>%html_attr("href")
straddr <- sapply(strsplit(staddrlink,"/"),function(x) x[3])

# get the area of lot

lotsqfttxt <- lapply(houselist,function(x) x%>%html_node(".property-lot")%>%html_text())
# comment for above line: 
# Ideally I want to use the following line instead of the line above
#
# lotsqfttxt=houselist%>%html_node(".property-lot")%>%html_text()
#
# however if certain houses don't have .property-lot, 
# then it returns lesser number of entries than number of houses
# This makes combining this data with other house data difficult
#

## extract numerical value of lot area in sqft (do unit conversion from acre to sqft if needed)
lotsqft <- sapply(lotsqfttxt,
                  function(x) {
                     if(length(x)==0){
                       xsqftnum=NA
                       return(xsqftnum)
                     } else {
                       xsplit=strsplit(x," ")[[1]]
                       xsqftnum=as.numeric(gsub(",","",xsplit[1]))
                       if ((tolower(xsplit[2]) == "ac") | (tolower(xsplit[2]) == "acre")) {
                         xsqftnum=xsqftnum*43560
                       }  
                     }
                     
                     return(xsqftnum)
                  })


# year house was built
yrbuilt <- houselist%>%html_node(".property-year")%>%html_text()%>%gsub("Built in ","",.)%>%as.numeric()

# price of house
price <- houselist%>%html_node(".price-large")%>%html_text()%>%gsub("[\\$a-zA-Z,]","",.)%>%as.numeric()

# house parameters (number of beds, baths, house area)
houseparams <- houselist%>%html_node(".property-data")%>%html_text()
houseparamsSplit <- strsplit(houseparams,", ")
## get number of beds
numbeds <- sapply(houseparamsSplit,function(x) as.numeric(strsplit(x[1]," ")[[1]][1]))
## get number of baths
numbaths <- sapply(houseparamsSplit,function(x) as.numeric(strsplit(x[2]," ")[[1]][1]))
## get house area in sqft (convert from acre to sqft if needed)
housesqft <- sapply(houseparamsSplit,
               function(x){
                 xsplit=strsplit(x[3]," ")[[1]]
                 xsqft=as.numeric(gsub(",","",xsplit[1]))
                 if((tolower(xsplit[2]) == "ac") | (tolower(xsplit[2]) == "acre")) {
                   # convert acre to sqft
                   xsqft=xsqft*43560
                 }
                 return(xsqft)
               })

# bring all the house variables together into a dataframe
houseData <- data.frame(zpid,price,yrbuilt,numbeds,numbaths,housesqft,lotsqft,straddr)

head(houseData)

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


```{r}
url <- "http://www.zillow.com/homes/for_sale/VT/58_rid/any_days/45.537137,-69.062805,42.187829,-75.846863_rect/7_zm/"
# I manually checked the source html to find the correct node to read
more.urls <- read_html(url) %>%
  html_nodes(".zsg-pagination a") %>%
  html_attr("href") 
# See how high the pagination goes
more.urls <- more.urls[!is.na(more.urls)]
more.urls <- strsplit(more.urls, '/')
more.urls <- lapply(more.urls, function(x) x[length(x)])
more.urls <- as.numeric(gsub('[_p]','', more.urls))
more.urls <- max(more.urls)
# Now paste together a url for each page
urls <- c(url, paste0(url,2:more.urls,'_p/'))

urls


```


```{r}
# The scraper function
getZillow <- function(urls) {
    # return a list of html <article></article> tags, one for each URL
    lapply(urls, function(u) {
        # call out the at-bat url in case there is an error
        cat(u, '\n')
        houses <- read_html(u) %>%
          html_nodes("article")
        houses
    })
}
zdata2 <- getZillow(urls)
as.character(zdata2[[1]][1])

```

```{r}
results <- xmlToList(zr_xml$response[["properties"]])

getValRange <- function(x, hilo) {
  ifelse(hilo %in% unlist(dimnames(x)), x["text",hilo][[1]], NA)
}

out <- apply(results, MAR=2, function(property) {
  zpid <- property$zpid
  links <- unlist(property$links)
  address <- unlist(property$address)
  z <- property$zestimate
  zestdf <- list(
    amount=ifelse("text" %in% names(z$amount), z$amount$text, NA),
    lastupdated=z$"last-updated",
    valueChange=ifelse(length(z$valueChange)==0, NA, z$valueChange),
    valueLow=getValRange(z$valuationRange, "low"),
    valueHigh=getValRange(z$valuationRange, "high"),
    percentile=z$percentile)  
  list(id=zpid, links, address, zestdf)
})

data <- as.data.frame(do.call(rbind, lapply(out, unlist)), 
  row.names=seq_len(length(out)))
```

###
unlist(results)
                                                                                 principal.zpid 
                                                                                      "9396682" 
                                                                    principal.links.homedetails 
               "https://www.zillow.com/homedetails/101-Dauphin-Dr-Media-PA-19063/9396682_zpid/" 
                                                                  principal.links.graphsanddata 
"http://www.zillow.com/homedetails/101-Dauphin-Dr-Media-PA-19063/9396682_zpid/#charts-and-data" 
                                                                    principal.links.mapthishome 
                                                    "http://www.zillow.com/homes/9396682_zpid/" 
                                                                    principal.links.comparables 
                                              "http://www.zillow.com/homes/comps/9396682_zpid/" 
                                                                       principal.address.street 
                                                                               "101 Dauphin Dr" 
                                                                      principal.address.zipcode 
                                                                                        "19063" 
                                                                         principal.address.city 
                                                                                        "Media" 
                                                                        principal.address.state 
                                                                                           "PA" 
                                                                     principal.address.latitude 
                                                                                    "39.938598" 
                                                                    principal.address.longitude 
                                                                                   "-75.367816" 
                                                                    principal.taxAssessmentYear 
                                                                                         "2018" 
                                                                        principal.taxAssessment 
                                                                                     "295200.0" 
                                                                            principal.yearBuilt 
                                                                                         "2012" 
                                                                          principal.lotSizeSqFt 
                                                                                       "348088" 
                                                                         principal.finishedSqFt 
                                                                                         "3652" 
                                                                            principal.bathrooms 
                                                                                          "3.0" 
                                                                             principal.bedrooms 
                                                                                            "3" 
                                                                           principal.totalRooms 
                                                                                            "8" 
                                                                         principal.lastSoldDate 
                                                                                   "01/02/2019" 
                                                                   principal.lastSoldPrice.text 
                                                                                       "528000" 
                                                        principal.lastSoldPrice..attrs.currency 
                                                                                          "USD" 
                                                                principal.zestimate.amount.text 
                                                                                       "536435" 
                                                     principal.zestimate.amount..attrs.currency 
                                                                                          "USD" 
                                                               principal.zestimate.last-updated 
                                                                                   "05/02/2019" 
                                                   principal.zestimate.oneWeekChange.deprecated 
                                                                                         "true" 
                                                           principal.zestimate.valueChange.text 
                                                                                         "2153" 
                                                principal.zestimate.valueChange..attrs.duration 
                                                                                           "30" 
                                                principal.zestimate.valueChange..attrs.currency 
                                                                                          "USD" 
                                                            principal.zestimate.valuationRange1 
                                                                                       "509613" 
                                                    principal.zestimate.valuationRange.currency 
                                                                                          "USD" 
                                                            principal.zestimate.valuationRange3 
                                                                                       "563257" 
                                                    principal.zestimate.valuationRange.currency 
                                                                                          "USD" 
                                                                 principal.zestimate.percentile 
                                                                                           "85" 
                                                                     principal.localRealEstate1 
                                                                                      "380,900" 
                                                             principal.localRealEstate.overview 
                                         "http://www.zillow.com/local-info/PA-Marple/r_398683/" 
                                                       principal.localRealEstate.forSaleByOwner 
                                                        "http://www.zillow.com/marple-pa/fsbo/" 
                                                              principal.localRealEstate.forSale 
                                                             "http://www.zillow.com/marple-pa/" 
                                                                 principal.localRealEstate.name 
                                                                                       "Marple" 
                                                                   principal.localRealEstate.id 
                                                                                       "398683" 
                                                                 principal.localRealEstate.type 
                                                                                         "city" 
                                                                                   comparables1 
                                                                                   "2087177793" 
                                                                        comparables.homedetails 
                 "https://www.zillow.com/homedetails/307-Avian-Media-PA-19063/2087177793_zpid/" 
                                                                        comparables.mapthishome 
                                                 "http://www.zillow.com/homes/2087177793_zpid/" 
                                                                        comparables.comparables 
                                           "http://www.zillow.com/homes/comps/2087177793_zpid/" 
                                                                             comparables.street 
                                                                                    "307 Avian" 
                                                                            comparables.zipcode 
                                                                                        "19063" 
                                                                               comparables.city 
                                                                                        "Media" 
                                                                              comparables.state 
                                                                                           "PA" 
                                                                           comparables.latitude 
                                                                                    "39.941449" 
                                                                          comparables.longitude 
                                                                                   "-75.366754" 
                                                                                  comparables11 
                                                                                         "2412" 
                                                                                  comparables12 
                                                                                          "4.0" 
                                                                                  comparables13 
                                                                                            "3" 
                                                                                  comparables14 
                                                                                   "10/30/2018" 
                                                                               comparables.text 
                                                                                       "421995" 
                                                                    comparables..attrs.currency 
                                                                                          "USD" 
                                                                        comparables.amount.text 
                                                                                       "470987" 
                                                             comparables.amount..attrs.currency 
                                                                                          "USD" 
                                                                       comparables.last-updated 
                                                                                   "05/02/2019" 
                                                           comparables.oneWeekChange.deprecated 
                                                                                         "true" 
                                                                   comparables.valueChange.text 
                                                                                        "-1290" 
                                                        comparables.valueChange..attrs.duration 
                                                                                           "30" 
                                                        comparables.valueChange..attrs.currency 
                                                                                          "USD" 
                                                                    comparables.valuationRange1 
                                                                                       "386209" 
                                                            comparables.valuationRange.currency 
                                                                                          "USD" 
                                                                    comparables.valuationRange3 
                                                                                       "626413" 
                                                            comparables.valuationRange.currency 
                                                                                          "USD" 
                                                                         comparables.percentile 
                                                                                            "0" 
                                                                                  comparables29 
                                                                                      "380,900" 
                                                                           comparables.overview 
                                         "http://www.zillow.com/local-info/PA-Marple/r_398683/" 
                                                                     comparables.forSaleByOwner 
                                                        "http://www.zillow.com/marple-pa/fsbo/" 
                                                                            comparables.forSale 
                                                             "http://www.zillow.com/marple-pa/" 
                                                                               comparables.name 
                                                                                       "Marple" 
                                                                                 comparables.id 
                                                                                       "398683" 
                                                                               comparables.type 
                                                                                         "city" 
                                                                              comparables.score 
                                                                                          "5.0" 
                                                                                  comparables37 
                                                                                   "2087223376" 
                                                                        comparables.homedetails 
          "https://www.zillow.com/homedetails/301-Corvus-Drive-Media-PA-19063/2087223376_zpid/" 
                                                                        comparables.mapthishome 
                                                 "http://www.zillow.com/homes/2087223376_zpid/" 
                                                                        comparables.comparables 
                                           "http://www.zillow.com/homes/comps/2087223376_zpid/" 
                                                                             comparables.street 
                                                                             "301 Corvus Drive" 
                                                                            comparables.zipcode 
                                                                                        "19063" 
                                                                               comparables.city 
                                                                                        "Media" 
                                                                              comparables.state 
                                                                                           "PA" 
                                                                           comparables.latitude 
                                                                                    "39.938611" 
                                                                          comparables.longitude 
                                                                                   "-75.366389" 
                                                                                  comparables47 
                                                                                         "3000" 
                                                                                  comparables48 
                                                                                          "3.0" 
                                                                                  comparables49 
                                                                                            "3" 
                                                                                  comparables50 
                                                                                   "10/26/2018" 
                                                                               comparables.text 
                                                                                       "423995" 
                                                                    comparables..attrs.currency 
                                                                                          "USD" 
                                                                        comparables.amount.text 
                                                                                       "514747" 
                                                             comparables.amount..attrs.currency 
                                                                                          "USD" 
                                                                       comparables.last-updated 
                                                                                   "05/02/2019" 
                                                           comparables.oneWeekChange.deprecated 
                                                                                         "true" 
                                                                   comparables.valueChange.text 
                                                                                        "-3712" 
                                                        comparables.valueChange..attrs.duration 
                                                                                           "30" 
                                                        comparables.valueChange..attrs.currency 
                                                                                          "USD" 
                                                                    comparables.valuationRange1 
                                                                                       "401503" 
                                                            comparables.valuationRange.currency 
                                                                                          "USD" 
                                                                    comparables.valuationRange3 
                                                                                       "612549" 
                                                            comparables.valuationRange.currency 
                                                                                          "USD" 
                                                                         comparables.percentile 
                                                                                            "0" 
                                                                                  comparables65 
                                                                                      "380,900" 
                                                                           comparables.overview 
                                         "http://www.zillow.com/local-info/PA-Marple/r_398683/" 
                                                                     comparables.forSaleByOwner 
                                                        "http://www.zillow.com/marple-pa/fsbo/" 
                                                                            comparables.forSale 
                                                             "http://www.zillow.com/marple-pa/" 
                                                                               comparables.name 
                                                                                       "Marple" 
                                                                                 comparables.id 
                                                                                       "398683" 
                                                                               comparables.type 
                                                                                         "city" 
                                                                              comparables.score 
                                                                                          "4.0" 
                                                                                  comparables73 
                                                                                   "2090552161" 
                                                                        comparables.homedetails 
             "https://www.zillow.com/homedetails/311-Avian-Aly-Media-PA-19063/2090552161_zpid/" 
                                                                        comparables.mapthishome 
                                                 "http://www.zillow.com/homes/2090552161_zpid/" 
                                                                        comparables.comparables 
                                           "http://www.zillow.com/homes/comps/2090552161_zpid/" 
                                                                             comparables.street 
                                                                                "311 Avian Aly" 
                                                                            comparables.zipcode 
                                                                                        "19063" 
                                                                               comparables.city 
                                                                                        "Media" 
                                                                              comparables.state 
                                                                                           "PA" 
                                                                           comparables.latitude 
                                                                                    "39.938611" 
                                                                          comparables.longitude 
                                                                                   "-75.366388" 
                                                                                  comparables83 
                                                                                         "2295" 
                                                                                  comparables84 
                                                                                          "2.5" 
                                                                                  comparables85 
                                                                                            "3" 
                                                                                  comparables86 
                                                                                   "11/29/2018" 
                                                                               comparables.text 
                                                                                       "449926" 
                                                                    comparables..attrs.currency 
                                                                                          "USD" 
                                                                        comparables.amount.text 
                                                                                       "440321" 
                                                             comparables.amount..attrs.currency 
                                                                                          "USD" 
                                                                       comparables.last-updated 
                                                                                   "05/02/2019" 
                                                           comparables.oneWeekChange.deprecated 
                                                                                         "true" 
                                                                   comparables.valueChange.text 
                                                                                       "-22059" 
                                                        comparables.valueChange..attrs.duration 
                                                                                           "30" 
                                                        comparables.valueChange..attrs.currency 
                                                                                          "USD" 
                                                                    comparables.valuationRange1 
                                                                                       "356660" 
                                                            comparables.valuationRange.currency 
                                                                                          "USD" 
                                                                    comparables.valuationRange3 
                                                                                       "550401" 
                                                            comparables.valuationRange.currency 
                                                                                          "USD" 
                                                                         comparables.percentile 
                                                                                            "0" 
                                                                                 comparables101 
                                                                                      "380,900" 
                                                                           comparables.overview 
                                         "http://www.zillow.com/local-info/PA-Marple/r_398683/" 
                                                                     comparables.forSaleByOwner 
                                                        "http://www.zillow.com/marple-pa/fsbo/" 
                                                                            comparables.forSale 
                                                             "http://www.zillow.com/marple-pa/" 
                                                                               comparables.name 
                                                                                       "Marple" 
                                                                                 comparables.id 
                                                                                       "398683" 
                                                                               comparables.type 
                                                                                         "city" 
                                                                              comparables.score 
                                                                                          "4.0" 
                                                                                 comparables109 
                                                                                   "2090932091" 
                                                                        comparables.homedetails 
             "https://www.zillow.com/homedetails/303-Avian-Aly-Media-PA-19063/2090932091_zpid/" 
                                                                        comparables.mapthishome 
                                                 "http://www.zillow.com/homes/2090932091_zpid/" 
                                                                        comparables.comparables 
                                           "http://www.zillow.com/homes/comps/2090932091_zpid/" 
                                                                             comparables.street 
                                                                                "303 Avian Aly" 
                                                                            comparables.zipcode 
                                                                                        "19063" 
                                                                               comparables.city 
                                                                                        "Media" 
                                                                              comparables.state 
                                                                                           "PA" 
                                                                           comparables.latitude 
                                                                                    "39.938611" 
                                                                          comparables.longitude 
                                                                                   "-75.366388" 
                                                                                 comparables119 
                                                                                         "2741" 
                                                                                 comparables120 
                                                                                          "2.5" 
                                                                                 comparables121 
                                                                                            "3" 
                                                                                 comparables122 
                                                                                   "11/28/2018" 
                                                                               comparables.text 
                                                                                       "447295" 
                                                                    comparables..attrs.currency 
                                                                                          "USD" 
                                                                        comparables.amount.text 
                                                                                       "487119" 
                                                             comparables.amount..attrs.currency 
                                                                                          "USD" 
                                                                       comparables.last-updated 
                                                                                   "05/02/2019" 
                                                           comparables.oneWeekChange.deprecated 
                                                                                         "true" 
                                                                   comparables.valueChange.text 
                                                                                        "-1985" 
                                                        comparables.valueChange..attrs.duration 
                                                                                           "30" 
                                                        comparables.valueChange..attrs.currency 
                                                                                          "USD" 
                                                                    comparables.valuationRange1 
                                                                                       "394566" 
                                                            comparables.valuationRange.currency 
                                                                                          "USD" 
                                                                    comparables.valuationRange3 
                                                                                       "594285" 
                                                            comparables.valuationRange.currency 
                                                                                          "USD" 
                                                                         comparables.percentile 
                                                                                            "0" 
                                                                                 comparables137 
                                                                                      "380,900" 
                                                                           comparables.overview 
                                         "http://www.zillow.com/local-info/PA-Marple/r_398683/" 
                                                                     comparables.forSaleByOwner 
                                                        "http://www.zillow.com/marple-pa/fsbo/" 
                                                                            comparables.forSale 
                                                             "http://www.zillow.com/marple-pa/" 
                                                                               comparables.name 
                                                                                       "Marple" 
                                                                                 comparables.id 
                                                                                       "398683" 
                                                                               comparables.type 
                                                                                         "city" 
                                                                              comparables.score 
                                                                                          "4.0" 
                                                                                 comparables145 
                                                                                   "2084804200" 
                                                                        comparables.homedetails 
                "https://www.zillow.com/homedetails/301-Murray-Media-PA-19063/2084804200_zpid/" 
                                                                        comparables.mapthishome 
                                                 "http://www.zillow.com/homes/2084804200_zpid/" 
                                                                        comparables.comparables 
                                           "http://www.zillow.com/homes/comps/2084804200_zpid/" 
                                                                             comparables.street 
                                                                                   "301 Murray" 
                                                                            comparables.zipcode 
                                                                                        "19063" 
                                                                               comparables.city 
                                                                                        "Media" 
                                                                              comparables.state 
                                                                                           "PA" 
                                                                           comparables.latitude 
                                                                                      "39.9417" 
                                                                          comparables.longitude 
                                                                                     "-75.3664" 
                                                                                 comparables155 
                                                                                         "2666" 
                                                                                 comparables156 
                                                                                          "3.0" 
                                                                                 comparables157 
                                                                                            "3" 
                                                                                 comparables158 
                                                                                   "02/08/2019" 
                                                                               comparables.text 
                                                                                       "489215" 
                                                                    comparables..attrs.currency 
                                                                                          "USD" 
                                                                        comparables.amount.text 
                                                                                       "469340" 
                                                             comparables.amount..attrs.currency 
                                                                                          "USD" 
                                                                       comparables.last-updated 
                                                                                   "05/02/2019" 
                                                           comparables.oneWeekChange.deprecated 
                                                                                         "true" 
                                                                    comparables.valuationRange1 
                                                                                       "380165" 
                                                            comparables.valuationRange.currency 
                                                                                          "USD" 
                                                                    comparables.valuationRange3 
                                                                                       "581982" 
                                                            comparables.valuationRange.currency 
                                                                                          "USD" 
                                                                         comparables.percentile 
                                                                                            "0" 
                                                                                 comparables170 
                                                                                      "380,900" 
                                                                           comparables.overview 
                                         "http://www.zillow.com/local-info/PA-Marple/r_398683/" 
                                                                     comparables.forSaleByOwner 
                                                        "http://www.zillow.com/marple-pa/fsbo/" 
                                                                            comparables.forSale 
                                                             "http://www.zillow.com/marple-pa/" 
                                                                               comparables.name 
                                                                                       "Marple" 
                                                                                 comparables.id 
                                                                                       "398683" 
                                                                               comparables.type 
                                                                                         "city" 
                                                                              comparables.score 
                                                                                          "2.0" 
> do.call(rbind, results)
                comp         comp         comp         comp         comp        
principal       "9396682"    List,4       List,6       "2018"       "295200.0"  
zpid            "2087177793" "2087223376" "2090552161" "2090932091" "2084804200"
links           List,3       List,3       List,3       List,3       List,3      
address         List,6       List,6       List,6       List,6       List,6      
finishedSqFt    "2412"       "3000"       "2295"       "2741"       "2666"      
bathrooms       "4.0"        "3.0"        "2.5"        "2.5"        "3.0"       
bedrooms        "3"          "3"          "3"          "3"          "3"         
lastSoldDate    "10/30/2018" "10/26/2018" "11/29/2018" "11/28/2018" "02/08/2019"
lastSoldPrice   List,2       List,2       List,2       List,2       List,2      
zestimate       List,6       List,6       List,6       List,6       List,6      
localRealEstate List,3       List,3       List,3       List,3       List,3      
.attrs          "5.0"        "4.0"        "4.0"        "4.0"        "2.0"       
Warning message:
In (function (..., deparse.level = 1)  :
  number of columns of result is not a multiple of vector length (arg 1)
> do.call(rbind, lapply(results,unlist))
                         homedetails                                                                     
principal   "9396682"    "https://www.zillow.com/homedetails/101-Dauphin-Dr-Media-PA-19063/9396682_zpid/"
comparables "2087177793" "https://www.zillow.com/homedetails/307-Avian-Media-PA-19063/2087177793_zpid/"  
            mapthishome                                                                                    
principal   "http://www.zillow.com/homedetails/101-Dauphin-Dr-Media-PA-19063/9396682_zpid/#charts-and-data"
comparables "http://www.zillow.com/homes/2087177793_zpid/"                                                 
            comparables                                          street                                            zipcode          city    state  
principal   "http://www.zillow.com/homes/9396682_zpid/"          "http://www.zillow.com/homes/comps/9396682_zpid/" "101 Dauphin Dr" "19063" "Media"
comparables "http://www.zillow.com/homes/comps/2087177793_zpid/" "307 Avian"                                       "19063"          "Media" "PA"   
            latitude    longitude                                                text     .attrs.currency amount.text amount..attrs.currency
principal   "PA"        "39.938598"  "-75.367816" "2018" "295200.0" "2012"       "348088" "3652"          "3.0"       "3"                   
comparables "39.941449" "-75.366754" "2412"       "4.0"  "3"        "10/30/2018" "421995" "USD"           "470987"    "USD"                 
            last-updated oneWeekChange.deprecated valueChange.text valueChange..attrs.duration valueChange..attrs.currency valuationRange1
principal   "8"          "01/02/2019"             "528000"         "USD"                       "536435"                    "USD"          
comparables "05/02/2019" "true"                   "-1290"          "30"                        "USD"                       "386209"       
            valuationRange.currency valuationRange3 valuationRange.currency percentile           overview                                              
principal   "05/02/2019"            "true"          "2153"                  "30"       "USD"     "509613"                                              
comparables "USD"                   "626413"        "USD"                   "0"        "380,900" "http://www.zillow.com/local-info/PA-Marple/r_398683/"
            forSaleByOwner                          forSale                            name     id       type     
principal   "USD"                                   "563257"                           "USD"    "85"     "380,900"
comparables "http://www.zillow.com/marple-pa/fsbo/" "http://www.zillow.com/marple-pa/" "Marple" "398683" "city"   
            score                                                                                         
principal   "http://www.zillow.com/local-info/PA-Marple/r_398683/" "http://www.zillow.com/marple-pa/fsbo/"
comparables "5.0"                                                  "2087223376"                           
            homedetails                                                                           mapthishome                                   
principal   "http://www.zillow.com/marple-pa/"                                                    "Marple"                                      
comparables "https://www.zillow.com/homedetails/301-Corvus-Drive-Media-PA-19063/2087223376_zpid/" "http://www.zillow.com/homes/2087223376_zpid/"
            comparables                                          street             zipcode  
principal   "398683"                                             "city"             "9396682"
comparables "http://www.zillow.com/homes/comps/2087223376_zpid/" "301 Corvus Drive" "19063"  
            city                                                                            
principal   "https://www.zillow.com/homedetails/101-Dauphin-Dr-Media-PA-19063/9396682_zpid/"
comparables "Media"                                                                         
            state                                                                                           latitude                                   
principal   "http://www.zillow.com/homedetails/101-Dauphin-Dr-Media-PA-19063/9396682_zpid/#charts-and-data" "http://www.zillow.com/homes/9396682_zpid/"
comparables "PA"                                                                                            "39.938611"                                
            longitude                                                                                       text        .attrs.currency amount.text
principal   "http://www.zillow.com/homes/comps/9396682_zpid/" "101 Dauphin Dr" "19063" "Media" "PA"         "39.938598" "-75.367816"    "2018"     
comparables "-75.366389"                                      "3000"           "3.0"   "3"     "10/26/2018" "423995"    "USD"           "514747"   
            amount..attrs.currency last-updated oneWeekChange.deprecated valueChange.text valueChange..attrs.duration valueChange..attrs.currency
principal   "295200.0"             "2012"       "348088"                 "3652"           "3.0"                       "3"                        
comparables "USD"                  "05/02/2019" "true"                   "-3712"          "30"                        "USD"                      
            valuationRange1 valuationRange.currency valuationRange3 valuationRange.currency percentile          
principal   "8"             "01/02/2019"            "528000"        "USD"                   "536435"   "USD"    
comparables "401503"        "USD"                   "612549"        "USD"                   "0"        "380,900"
            overview                                               forSaleByOwner                          forSale                            name    
principal   "05/02/2019"                                           "true"                                  "2153"                             "30"    
comparables "http://www.zillow.com/local-info/PA-Marple/r_398683/" "http://www.zillow.com/marple-pa/fsbo/" "http://www.zillow.com/marple-pa/" "Marple"
            id       type     score              homedetails                                                                       
principal   "USD"    "509613" "USD" "563257"     "USD"                                                                             
comparables "398683" "city"   "4.0" "2090552161" "https://www.zillow.com/homedetails/311-Avian-Aly-Media-PA-19063/2090552161_zpid/"
            mapthishome                                    comparables                                         
principal   "85"                                           "380,900"                                           
comparables "http://www.zillow.com/homes/2090552161_zpid/" "http://www.zillow.com/homes/comps/2090552161_zpid/"
            street                                                 zipcode                                 city                               state   
principal   "http://www.zillow.com/local-info/PA-Marple/r_398683/" "http://www.zillow.com/marple-pa/fsbo/" "http://www.zillow.com/marple-pa/" "Marple"
comparables "311 Avian Aly"                                        "19063"                                 "Media"                            "PA"    
            latitude    longitude                                                                                              
principal   "398683"    "city"       "9396682" "https://www.zillow.com/homedetails/101-Dauphin-Dr-Media-PA-19063/9396682_zpid/"
comparables "39.938611" "-75.366388" "2295"    "2.5"                                                                           
                                                                                                                                                       
principal   "http://www.zillow.com/homedetails/101-Dauphin-Dr-Media-PA-19063/9396682_zpid/#charts-and-data" "http://www.zillow.com/homes/9396682_zpid/"
comparables "3"                                                                                             "11/29/2018"                               
            text                                              .attrs.currency  amount.text amount..attrs.currency last-updated oneWeekChange.deprecated
principal   "http://www.zillow.com/homes/comps/9396682_zpid/" "101 Dauphin Dr" "19063"     "Media"                "PA"         "39.938598"             
comparables "449926"                                          "USD"            "440321"    "USD"                  "05/02/2019" "true"                  
            valueChange.text valueChange..attrs.duration valueChange..attrs.currency valuationRange1 valuationRange.currency valuationRange3
principal   "-75.367816"     "2018"                      "295200.0"                  "2012"          "348088"                "3652"         
comparables "-22059"         "30"                        "USD"                       "356660"        "USD"                   "550401"       
            valuationRange.currency percentile           overview                                               forSaleByOwner                         
principal   "3.0"                   "3"        "8"       "01/02/2019"                                           "528000"                               
comparables "USD"                   "0"        "380,900" "http://www.zillow.com/local-info/PA-Marple/r_398683/" "http://www.zillow.com/marple-pa/fsbo/"
            forSale                            name     id       type         score              
principal   "USD"                              "536435" "USD"    "05/02/2019" "true" "2153"      
comparables "http://www.zillow.com/marple-pa/" "Marple" "398683" "city"       "4.0"  "2090932091"
            homedetails                                                                        mapthishome                                   
principal   "30"                                                                               "USD"                                         
comparables "https://www.zillow.com/homedetails/303-Avian-Aly-Media-PA-19063/2090932091_zpid/" "http://www.zillow.com/homes/2090932091_zpid/"
            comparables                                          street          zipcode  city    state latitude   
principal   "509613"                                             "USD"           "563257" "USD"   "85"  "380,900"  
comparables "http://www.zillow.com/homes/comps/2090932091_zpid/" "303 Avian Aly" "19063"  "Media" "PA"  "39.938611"
            longitude                                                                                                                                 
principal   "http://www.zillow.com/local-info/PA-Marple/r_398683/" "http://www.zillow.com/marple-pa/fsbo/" "http://www.zillow.com/marple-pa/" "Marple"
comparables "-75.366388"                                           "2741"                                  "2.5"                              "3"     
                         text     .attrs.currency amount.text                                                                     
principal   "398683"     "city"   "9396682"       "https://www.zillow.com/homedetails/101-Dauphin-Dr-Media-PA-19063/9396682_zpid/"
comparables "11/28/2018" "447295" "USD"           "487119"                                                                        
            amount..attrs.currency                                                                          last-updated                               
principal   "http://www.zillow.com/homedetails/101-Dauphin-Dr-Media-PA-19063/9396682_zpid/#charts-and-data" "http://www.zillow.com/homes/9396682_zpid/"
comparables "USD"                                                                                           "05/02/2019"                               
            oneWeekChange.deprecated                          valueChange.text valueChange..attrs.duration valueChange..attrs.currency valuationRange1
principal   "http://www.zillow.com/homes/comps/9396682_zpid/" "101 Dauphin Dr" "19063"                     "Media"                     "PA"           
comparables "true"                                            "-1985"          "30"                        "USD"                       "394566"       
            valuationRange.currency valuationRange3 valuationRange.currency percentile           overview                                              
principal   "39.938598"             "-75.367816"    "2018"                  "295200.0" "2012"    "348088"                                              
comparables "USD"                   "594285"        "USD"                   "0"        "380,900" "http://www.zillow.com/local-info/PA-Marple/r_398683/"
            forSaleByOwner                          forSale                            name     id       type         score                
principal   "3652"                                  "3.0"                              "3"      "8"      "01/02/2019" "528000" "USD"       
comparables "http://www.zillow.com/marple-pa/fsbo/" "http://www.zillow.com/marple-pa/" "Marple" "398683" "city"       "4.0"    "2084804200"
            homedetails                                                                     mapthishome                                   
principal   "536435"                                                                        "USD"                                         
comparables "https://www.zillow.com/homedetails/301-Murray-Media-PA-19063/2084804200_zpid/" "http://www.zillow.com/homes/2084804200_zpid/"
            comparables                                          street       zipcode city    state latitude  longitude                     
principal   "05/02/2019"                                         "true"       "2153"  "30"    "USD" "509613"  "USD"      "563257" "USD" "85"
comparables "http://www.zillow.com/homes/comps/2084804200_zpid/" "301 Murray" "19063" "Media" "PA"  "39.9417" "-75.3664" "2666"   "3.0" "3" 
                         text                                                   .attrs.currency                        
principal   "380,900"    "http://www.zillow.com/local-info/PA-Marple/r_398683/" "http://www.zillow.com/marple-pa/fsbo/"
comparables "02/08/2019" "489215"                                               "USD"                                  
            amount.text                        amount..attrs.currency last-updated oneWeekChange.deprecated valuationRange1
principal   "http://www.zillow.com/marple-pa/" "Marple"               "398683"     "city"                   "9396682"      
comparables "469340"                           "USD"                  "05/02/2019" "true"                   "380165"       
            valuationRange.currency                                                         
principal   "https://www.zillow.com/homedetails/101-Dauphin-Dr-Media-PA-19063/9396682_zpid/"
comparables "USD"                                                                           
            valuationRange3                                                                                 valuationRange.currency                    
principal   "http://www.zillow.com/homedetails/101-Dauphin-Dr-Media-PA-19063/9396682_zpid/#charts-and-data" "http://www.zillow.com/homes/9396682_zpid/"
comparables "581982"                                                                                        "USD"                                      
            percentile                                                         overview                                              
principal   "http://www.zillow.com/homes/comps/9396682_zpid/" "101 Dauphin Dr" "19063"                                               
comparables "0"                                               "380,900"        "http://www.zillow.com/local-info/PA-Marple/r_398683/"
            forSaleByOwner                          forSale                            name        id           type   score     
principal   "Media"                                 "PA"                               "39.938598" "-75.367816" "2018" "295200.0"
comparables "http://www.zillow.com/marple-pa/fsbo/" "http://www.zillow.com/marple-pa/" "Marple"    "398683"     "city" "2.0"     
Warning message:
In (function (..., deparse.level = 1)  :
  number of columns of result is not a multiple of vector length (arg 1)
> data_frame(do.call(rbind, lapply(results,unlist)))
# A tibble: 2 x 1
  `do.call(rbind,~ [,"homedetails"] [,"mapthishome"] [,"comparables"] [,"street"] [,"zipcode"] [,"city"] [,"state"] [,"latitude"] [,"longitude"] [,""]
  <chr>            <chr>            <chr>            <chr>            <chr>       <chr>        <chr>     <chr>      <chr>         <chr>          <chr>
1 9396682          https://www.zil~ http://www.zill~ http://www.zill~ http://www~ 101 Dauphin~ 19063     Media      PA            39.938598      -75.~
2 2087177793       https://www.zil~ http://www.zill~ http://www.zill~ 307 Avian   19063        Media     PA         39.941449     -75.366754     2412 
# ... with 166 more variables: [,""] <chr>, [,""] <chr>, [,""] <chr>, [,"text"] <chr>, [,".attrs.currency"] <chr>, [,"amount.text"] <chr>,
#   [,"amount..attrs.currency"] <chr>, [,"last-updated"] <chr>, [,"oneWeekChange.deprecated"] <chr>, [,"valueChange.text"] <chr>,
#   [,"valueChange..attrs.duration"] <chr>, [,"valueChange..attrs.currency"] <chr>, [,"valuationRange1"] <chr>, [,"valuationRange.currency"] <chr>,
#   [,"valuationRange3"] <chr>, [,"valuationRange.currency"] <chr>, [,"percentile"] <chr>, [,""] <chr>, [,"overview"] <chr>, [,"forSaleByOwner"] <chr>,
#   [,"forSale"] <chr>, [,"name"] <chr>, [,"id"] <chr>, [,"type"] <chr>, [,"score"] <chr>, [,""] <chr>, [,"homedetails"] <chr>, [,"mapthishome"] <chr>,
#   [,"comparables"] <chr>, [,"street"] <chr>, [,"zipcode"] <chr>, [,"city"] <chr>, [,"state"] <chr>, [,"latitude"] <chr>, [,"longitude"] <chr>,
#   [,""] <chr>, [,""] <chr>, [,""] <chr>, [,""] <chr>, [,"text"] <chr>, [,".attrs.currency"] <chr>, [,"amount.text"] <chr>,
#   [,"amount..attrs.currency"] <chr>, [,"last-updated"] <chr>, [,"oneWeekChange.deprecated"] <chr>, [,"valueChange.text"] <chr>,
#   [,"valueChange..attrs.duration"] <chr>, [,"valueChange..attrs.currency"] <chr>, [,"valuationRange1"] <chr>, [,"valuationRange.currency"] <chr>,
#   [,"valuationRange3"] <chr>, [,"valuationRange.currency"] <chr>, [,"percentile"] <chr>, [,""] <chr>, [,"overview"] <chr>, [,"forSaleByOwner"] <chr>,
#   [,"forSale"] <chr>, [,"name"] <chr>, [,"id"] <chr>, [,"type"] <chr>, [,"score"] <chr>, [,""] <chr>, [,"homedetails"] <chr>, [,"mapthishome"] <chr>,
#   [,"comparables"] <chr>, [,"street"] <chr>, [,"zipcode"] <chr>, [,"city"] <chr>, [,"state"] <chr>, [,"latitude"] <chr>, [,"longitude"] <chr>,
#   [,""] <chr>, [,""] <chr>, [,""] <chr>, [,""] <chr>, [,"text"] <chr>, [,".attrs.currency"] <chr>, [,"amount.text"] <chr>,
#   [,"amount..attrs.currency"] <chr>, [,"last-updated"] <chr>, [,"oneWeekChange.deprecated"] <chr>, [,"valueChange.text"] <chr>,
#   [,"valueChange..attrs.duration"] <chr>, [,"valueChange..attrs.currency"] <chr>, [,"valuationRange1"] <chr>, [,"valuationRange.currency"] <chr>,
#   [,"valuationRange3"] <chr>, [,"valuationRange.currency"] <chr>, [,"percentile"] <chr>, [,""] <chr>, [,"overview"] <chr>, [,"forSaleByOwner"] <chr>,
#   [,"forSale"] <chr>, [,"name"] <chr>, [,"id"] <chr>, [,"type"] <chr>, [,"score"] <chr>, [,""] <chr>, [,"homedetails"] <chr>, [,"mapthishome"] <chr>,
#   ...
Warning message:
In (function (..., deparse.level = 1)  :
  number of columns of result is not a multiple of vector length (arg 1)



```{r}
# turn off axis elements in ggplot for better visual comparison
newTheme <- list(theme(line = element_blank(),
      axis.text.x = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks = element_blank(), # turn off ticks
      axis.title.x = element_blank(), # turn off titles
      axis.title.y = element_blank(),
      legend.position = "none")) # turn off legend
```


```{r}
# read shapefile
paBound <- readOGR(".", "ZillowNeighborhoods-PA")
# convert to dataframe
paBound_df <- fortify(paBound)
```


```{r}
# plot map using ggplot
paMap <- ggplot(paBound_df, aes(long,lat, group = group)) +
  geom_polygon() +
  coord_equal() +
  labs(x = "Longitude (Degrees)",
       y = "Latitude (Degrees)",
      title = "PA Map Neighborhood ",
      subtitle = "WGS84 Datum, Units: Degrees - Latitude / Longitude") +
  scale_x_continuous(limits=c(-80.25,-79.75)) +
  scale_y_continuous(limits=c(40.255, 40.55))

paMap
```



a <- do.call(rbind, do.call(rbind, acs_t$geometry))
2. create a geo.set using the geo.make() function (see section 4.2);
3. optionally, use the acs.lookup() function to explore the variables you may want to download (see section 4.3.3 on page 20) ;
4. use the acs.fetch() function to download data for your new geography (see section 4.3.1 on page 16); 

As a teaser, here you can see one single command that will download ACS data on Place of Birth for the Foreign-Born Population in the United States
for every tract in all four PSRC counties:
> lots.o.data=acs.fetch(geo=geo.make(state="WA", county=c(33,35,53,61), tract="*"), table.number="B05006")

```{r}
 utah = readOGR(".", "ZillowNeighborhoods-PA")
  # utah@data$id = rownames(utah@data)
  # utah.points = fortify(utah, region="id")
  # utah.df = join(utah.points, utah@data, by="id")

ggplot(utah.df) + 
  aes(long,lat,group=group,fill=LEVEL3_NAM) + 
  geom_polygon() +
  geom_path(color="white") +
  coord_equal() +
  scale_fill_brewer("Utah Ecoregion")

or

utah.points = fortify.SpatialPolygonsDataFrame(utah, region="LEVEL3")
  names(utah.points)[which(names(utah.points)=="id")] = "LEVEL3"
  utah.df = join(utah.points, utah@data, by="LEVEL3")
  ggplot(utah.df) + 
    aes(long,lat,group=group,fill=LEVEL3_NAM) + 
    geom_polygon(data=subset(utah.df,LEVEL3!=19)) +
    geom_polygon(data=subset(utah.df,LEVEL3==19)) +
    geom_path(color="white") +
    coord_equal() +
    scale_fill_brewer("Utah Ecoregion")

```


```{r}
pal <- colorBin("Greens", domain = acs_value$estimate, n = 9)

acs_value %>%
    st_transform(crs = "+init=epsg:4326") %>%
    leaflet() %>%s
    addProviderTiles(provider = "CartoDB.Positron") %>%
    addPolygons(popup = ~ str_extract(NAME, "^([^,]*)"),
                stroke = FALSE,
                smoothFactor = 0,
                fillOpacity = 1,
                color = ~ pal(estimate)) %>%
    addLegend("bottomright", 
              pal = pal, 
              values = ~ estimate,
              title = "Median House Value",
              opacity = 1)
```